Comparing ChatGPT-4 to Physicians for Assigning Causes of Death from Verbal Autopsy: A Case Study of 6939 Deaths in Sierra Leone from 2019-2022

### 2024-02-09 manuscript/manuscript.tex
Add python and r code versions

\noindent For InterVA-5 and InSilicoVA, the standardized questionnaire data from the HEAL-SL EVA were first converted into 2016 World Health Organization (WHO) VA questionnaire revision 1.5.1 Open Data Kit (ODK) format \cite{worldhealthorganizationODKVerbalAutopsy2022,nafundiODKCollectData2023} consisting of 526 variables \cite{dipasqualeReleaseODK20162016}, followed by further conversion into OpenVA format \cite{liOpenVAToolkitVerbal2023} consisting of 353 variables \cite{byassInterVA5UserGuide2020} using the \verb|pyCrossVA| Python package \cite{thomasPycrossvaPrepareData}. The 6939 records were all converted into OpenVA formatted records for InterVA-5 and InSilicoVA.

@@

The ChatGPT-3.5 and ChatGPT-4 Application Programming Interface (API) was accessed using Python 3.12 and used to assign CODs for each record. ChatGPT-3.5 used the \verb|gpt-3.5-turbo| model, while ChatGPT-4 used the \verb|gpt-4-0613| mode. The parameter \verb|top_p| for ChatGPT-3.5 and ChatGPT-4, representing the sampling temperature, was set to 0.3 to consider only the top 30\% probability mass from the token results \cite{openaiOpenAIPlatformAPI2024}. Higher values closer to 1 may make the results more random, while lower values closer to 0 make the results more focused.

>>>>

\noindent For InterVA-5 and InSilicoVA, the standardized questionnaire data from the HEAL-SL EVA were first converted into 2016 World Health Organization (WHO) VA questionnaire revision 1.5.1 Open Data Kit (ODK) format \cite{worldhealthorganizationODKVerbalAutopsy2022,nafundiODKCollectData2023} consisting of 526 variables \cite{dipasqualeReleaseODK20162016}, followed by further conversion into OpenVA format \cite{liOpenVAToolkitVerbal2023} consisting of 353 variables \cite{byassInterVA5UserGuide2020} using the \verb|pyCrossVA| version 0.97 Python package \cite{thomasPycrossvaPrepareData}. The 6939 records were all converted into OpenVA formatted records for InterVA-5 and InSilicoVA.

@@

The ChatGPT-3.5 and ChatGPT-4 Application Programming Interface (API) was accessed using Python version 3.11.4 and used to assign CODs for each record. ChatGPT-3.5 used the \verb|gpt-3.5-turbo| model, while ChatGPT-4 used the \verb|gpt-4-0613| mode. The parameter \verb|top_p| for ChatGPT-3.5 and ChatGPT-4, representing the sampling temperature, was set to 0.3 to consider only the top 30\% probability mass from the token results \cite{openaiOpenAIPlatformAPI2024}. Higher values closer to 1 may make the results more random, while lower values closer to 0 make the results more focused.
